### 2023-09-15 main.tex
lll

	\partial \rho_{a}(x,t)=\sigma_{11}\Delta_{L}\rho_{a}(x,t)+\sigma_{12}\Delta_{L}\rho_{\overline{a}}(x,t)+\Upsilon\left(\rho_{\overline{a}}(x,t)-\rho_{a}(x,t)\right)

@@

		\item Is it possible to extend the results to a case with arbitrary number of species $N\in \mathbb{N}$ and arbitrary maximal site occupation $\nu\in \mathbb{N}$?

@@

The aim of this section is to answer to these questions. We first define the process on a chain in order to obtain average occupation evolution equations with $N-1$ discrete Laplacians and a reaction term. Second we construct the Lie algebraic description and we use it to prove absorbing duality in this general case. 

@@

	\mathcal{L}_{x,x+1}^{rd}=\sigma_{11}\mathcal{L}_{x,x+1}+\sigma_{12}\sum_{c=1}^{N-2}\mathcal{L}_{x,x+1}^{c}+(\Upsilon-2\nu\sigma_{12})\mathcal{L}_{x,x+1}^{m}

@@

	\mathcal{L}_{x,x+1}^{m}f(\bm{n})=\sum_{a,b=1}^{N}n_{a}^{x}\left(f(\bm{n}-\bm{\delta}_{a}^{x}+\bm{\delta}_{b}^{x})-f(\bm{n})\right)
The site generator reads

@@

where the boundary parameters are defined as

@@

		\alpha_{a}&=\sigma_{11}\rho_{a}^{L}+\sigma_{12}\sum_{b=2\,:\,b\neq a}^{N}\rho_{b}^{x}\qquad \text{if} \quad k\in \{2,\ldots,N\}\\

@@

and where, for every $x\in V$, we further assume that
	\sum_{a=1}^{N}\rho_{a}^{x}=\nu

@@

\textbf{Remark}: observe that the site generator $\mathcal{L}_{left}^{rd}$ has the form of the one of the multi-species stirring process \eqref{siteGenerator}. We wrote it with the uppercase 'rd' in order to underline the fact that we need a specific choice of the reservoirs parameters $\alpha_{a}$, as specified above. 

@@

	\mathcal{L}_{x,y}^{m}n_{d}^{x}=\sum_{a,b=2}^{N}n_{a}^{x}\left((n_{d}^{x}-\bm{\delta}_{a}^{x}+\bm{\delta}_{b}^{x})-n_{d}^{x}\right)=\sum_{b=1}^{N}(n_{b}^{x}-n_{d}^{x})

@@

Using equation \eqref{actionGraphRD} we have that $\forall x\in \{2,\ldots,L-1\}$ and $\forall d\in\{2,\ldots,N\}$

@@

	\mathcal{L}^{rd}n_{d}^{x}=\nu\sigma_{11}\Delta_{L}n_{d}^{x}+\nu\sigma_{12}\sum_{c=2\,:\,c\neq d}^{N}\Delta_{L}n_{c}^{x}+\Upsilon\sum_{c=2}^{N}(n_{c}^{x}-n_{\alpha}^{x})

@@

	\mathcal{L}^{rd}n_{d}^{1}=\sigma_{11}\nu \left(\rho_{d}^{1}-2n_{d}^{1}+n_{2}^{2}\right)+\sigma_{12}\nu\sum_{c=2\,:\,c\neq d}^{N}\left(\rho_{c}^{1}-2n_{c}^{1}+n_{c}^{2}\right)+\Upsilon\sum_{c=2\,:\,c\neq d}^{N}\left(n_{c}^{1}-n_{d}^{1}\right)
On the occupation variable $n_{d}^{L}$ the action is similar, but with the upper case $1$ replaced by $L$.\\ In the spirit of \cite{casini2022uphill} we can define the average density occupation of species $a$ at site $x$ as

@@

	\rho=\rho_{a}=\frac{\alpha}{\alpha_{N}+(N-1)\alpha}\quad \forall a\in \{1,\ldots,N-1\}\qquad \text{and}\qquad \rho_{N}=\frac{\alpha_{N}}{\alpha_{1}+(N-1)\alpha}

@@

	\Lambda_{rev}^{x}(n^{x})=\frac{\nu!}{\prod_{a=1}^{N}n_{a}^{x}!}\rho^{\sum_{a=1}^{N-1}n_{a}^{x}}\rho_{1}^{n_{1}^{x}}
This can be proved just by imposing the detailed balance conditions for the edge $x,x+1$ and for the boundary generators. For fixed edge $x\in \{1,\ldots,L\}$ we only prove the detailed balance for  $\mathcal{L}_{x,x+1}^{c}$ with $c\in\{1,\ldots,N-2\}$ since for the other generators the computation is similar. Consider the transition $\bm{n}\to \bm{n}-\delta_{a}^{x}+\delta_{g_{c}(b)}^{x}+\delta_{g_{c}(b)}^{x+1}-\delta_{b}^{x+1}$; the detailled balance reads

@@

that is true if and only if $\rho_{a}=\rho$ $\forall a\in \{2,\ldots,N\}$.\\

@@

For the boundary transitions we have that, analogously to what happens for the multispecies stirring process, the reservoirs parameters must be such that $\beta_{a}=\alpha_{a}$ and $\rho_{a}=\frac{\alpha_{a}}{|\alpha|}$. As a consequence we have the result. 

@@

	\bm{\xi}=\left(\xi_{2}^{0},\ldots,\xi_{N}^{0}\right)\otimes\left(\xi_{1}^{x},\ldots,\xi_{N}^{x}\right)^{\otimes L}\otimes \left(\xi_{1}^{L+1},\ldots,\xi_{N}^{L+1}\right)

@@

and the component $\xi_{a}^{0}$  gives the number of dual particles of type $a\in \{1,\ldots,N-1\}$ at 

@@

	D(\bm{n},\bm{\xi})=\prod_{a=1}^{N-1}\left(\rho_{a}^{L}\right)^{\xi_{a}^{0}}\left(\prod_{x=1}^{L}\frac{(\nu -\sum_{a=2}^{N}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\right)\prod_{a=1}^{N-1}\left(\rho_{a}^{R}\right)^{\xi_{a}^{L+1}}

@@

\textbf{Remark}: the generator $\mathcal{L}^{rd}$ has a dual $\widetilde{\mathcal{L}}^{rd}$ with respect to the same duality function \eqref{dualityElements} of the multi-species stirring process. The dual process has absorbing boundaries while it performs the same edge dynamics of $\mathcal{L}^{rd}$. As we will show this follows from a $gl(N)$ algebraic structure. 

@@

@@

Similarly, we will define the dual Hamiltonian $\widetilde{H}^{rd}$. For the edge dynamics, the original and the dual Hamiltonians do coincide, while the boundary ones are again $\widetilde{H}_{left},H_{right}$ defined in \eqref{siteDualHamiltonian}, but with the parameters introduced in \eqref{boundaryParamRD}.\\ We aim to show
\begin{equation}\label{DualityRelationRD}
	(H^{rd})^{T}D=D\widetilde{H}^{rd}
Therefore, we need to prove that, for arbitrary $x\in\{1,\ldots,L\}$
	(\mathcal{H}_{x,x+1}^{rd})^{T}D&=D\mathcal{H}_{x,x+1}^{rd}\label{edgeDualityRelationRD}\\
	H_{left}^{T}D&=D\widetilde{H}_{left}D\label{siteDualityRelationRD}
and similarly for $H_{right}$.
The duality matrix $D$ is again \eqref{dualityMatrix}. As already pointed out, $H_{left}$ and $\widetilde{H}_{left}$ have the same structure (up to a specific choice of the reservoirs parameters) therefore the duality relation for the boundaries is proved. However, $\mathcal{H}_{x,x+1}^{rd}$ has two more terms $\sum_{c=1}^{N-2}\mathcal{H}_{x,x+1}^{c}$ and $\mathcal{H}_{x,x+1}^{m}$. Therefore, we only need to show that 

@@

Since the matrix $R_{x}$ is the same, we shall show that $\mathcal{H}_{x,x+1}^{c}$ and $\mathcal{H}_{x,x+1}^{m}$ have $\exp{(E^{x})}\exp{(E^{x})}$ as a symmetry. The first result will follow from the commutator between $\mathcal{H}_{x,x+1}^{c}$ and $\sum_{d=1}^{N-1}(E_{dN}^{x})\otimes \sum_{k=1}^{N-1}E_{bN}^{x}$. Using \eqref{eq:comgl}, the bilinearity and associativity of the Kronecker product and the bilinearity of the brackets we obtain 

@@

With this prove we answered the second and third questions stated at the beginning of this section. \\

@@

The steady state $|\Psi\rangle$ of the Hamiltonian $H$ is given by 
\begin{equation}\label{steadyStateH}
	|\Psi\rangle=\sum_{\tau_{1},\ldots,\tau_{L}=1}^{N}\Psi(\bm{\tau})|\bm{\tau}\rangle
\end{equation}
where for every $(\tau_{1},\ldots,\tau_{L})=\bm{\tau}$
\begin{equation}
	\begin{split}
		\Psi(\bm{\tau})&=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{\tau_{y}}^{(1-c_{y})(1-\delta_{\tau_{y},N})}
		\\&+
		\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{\tau_{q_{r}},N}\right) 
		\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{d_{q_{b}}=2}^{N}
		\\&
		\sum_{c_{1}=0}^{1-\delta_{\eta_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\eta_{L},N}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\eta_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{\eta_{y}}^{(1-c_{y})(1-\delta_{\eta_{y},N})}
	\end{split}
\end{equation}
where we have introduced, $\forall x\in \{1,\ldots,L\}$
\begin{equation}
	\eta_{x}(b)=\begin{cases}
		\tau_{x}\qquad &\text{if}\quad x\notin \{q_{1},\ldots,q_{b}\}\\
		d_{x}\qquad &\text{otherwise}
	\end{cases}%\qquad \theta_{x}=\begin{cases}
		%\tau_{x}\qquad &\text{if}\quad x\neq 1,\ldots,b\\
		%	1 \qquad &\text{otherwise}
		%\end{cases}
	\end{equation}
	The dependence of $\eta_{x}(b)$ with respect to $b$ is usually understood for the sake of notation. 
	{\color{blue}
		\begin{equation}\label{steadyStateH-coeff}
			\begin{split}
				\Psi(\bm{\tau})&=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{\tau_{y}}^{(1-c_{y})(1-\delta_{\tau_{y},N})}
				\\&+
				\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{s=1}^{b}\delta_{s_{q_{r}},N}\right) 
				\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{d_{q_{b}}=2}^{N}
				\\&
				\sum_{x=1\,:\, x\neq q_{1},\ldots,q_{b}}^{L}\sum_{c_{x}=0}^{1-\delta_{\tau_{x},N}}\sum_{c_{q_{1}}=1}^{1}\ldots\sum_{c_{q_{b}}=0}^{1}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(2+L)}
				\prod_{y=1\,:\, y\neq q_{1},\ldots,q_{b}}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}
				\\ &
				\beta_{\tau_{y}}^{(1-c_{y})(1-\delta_{\tau_{y},N})}
				\prod_{t=1}^{b}\lambda_{d_{q_{t}}}\left(2+L-q_{t}-\sum_{j=q_{t}}^{L}c_{j}\right)^{c_{q_{t}}}\beta_{d_{q_{t}}}^{(1-c_{q_{t}})}
			\end{split}
		\end{equation}
	}
	\textbf{Remark}: we observe that if no holes are present in \eqref{steadyStateH-coeff}, i.e. if $\tau_{x}\neq 1$ $\forall x\in \{1,\ldots,L\}$, then the second addend vanishes and
	\begin{equation}\label{LinkABS-corr}
		\Psi(\bm{\tau})=\Psi^{'}(\bm{\tau})
	\end{equation}
	When the configuration has holes, the presence of the second addend is motivated by the dependence of the "empty" in a fixed site from all others types in the same site.

>>>>

	\frac{d}{dt} \rho_{a}(x,t)=\sigma_{11}\Delta_{L}\rho_{a}(x,t)+\sigma_{12}\Delta_{L}\rho_{\overline{a}}(x,t)+\Upsilon\left(\rho_{\overline{a}}(x,t)-\rho_{a}(x,t)\right)

@@

		\item Is it possible to extend the results of \cite{casini2022uphill} to a case with arbitrary number of species $N\in \mathbb{N}$ and arbitrary maximal site occupation $\nu\in \mathbb{N}$?

@@

Therefore, we aim to find a process whose average occupations $\rho_{a}(x,t)$ for any species $a\in\{1,\ldots,N-1\}$ evolve as a system of difference differential equation given by 
\begin{equation}\label{NSpeciesRD}
	\frac{d}{dt} \rho_{a}(x,t)=\nu\sigma_{11}\Delta_{L}\rho_{a}(x,t)+\nu\sigma_{12}\sum_{b=1,b\neq a}^{N-1}\Delta_{L}\rho_{b}(x,t)+\Upsilon\sum_{b=1,b\neq a}^{N-1}\left(\rho_{b}(x,t)-\rho_{a}(x,t)\right)
 We assume that the boundary conditions of the above difference differential system are given and denoted by $\rho_{a}^{L}$ and $\rho_{a}^{R}$ for all $a\in\{1,\ldots,N\}$ at left and right respectively, further assuming that $\sum_{a=1}^{N}\rho_{a}^{L}=\nu$.
In the following of this section we answer to these questions. We first define the process on a chain in order to obtain \eqref{NSpeciesRD} for the evolution of the average occupation variable of type $a$. Once we have found such a process, we construct the Lie algebraic description and we use it to prove absorbing duality in this general case. 

@@

	\mathcal{L}_{x,x+1}^{rd}=\nu \sigma_{11}\mathcal{L}_{x,x+1}+\nu \sigma_{12}\sum_{c=1}^{N-2}\mathcal{L}_{x,x+1}^{c}+(\Upsilon-2\nu\sigma_{12})\mathcal{L}_{x,x+1}^{m}

@@

	\mathcal{L}_{x,x+1}^{m}f(\bm{n})=\sum_{a,b=1}^{N-1}n_{a}^{x}\left(f(\bm{n}-\bm{\delta}_{a}^{x}+\bm{\delta}_{b}^{x})-f(\bm{n})\right)
The left boundary generator reads

@@

where the $\alpha$'s parameters are defined in function of the given boundary condition of the difference-differential system:

@@

		\alpha_{a}&=\sigma_{11}\rho_{a}^{L}+\sigma_{12}\sum_{b=2\,:\,b\neq a}^{N}\rho_{b}^{L}\qquad \text{if} \quad a\in \{1,\ldots,N-1\}\\

@@

@@

\textbf{Remark}: observe that, up to a specific choice of the $\alpha$'s, the left boundary generator $\mathcal{L}_{left}^{rd}$ has the form of the one of the multi-species stirring process \eqref{siteGenerator}. 

@@

	\mathcal{L}_{x,y}^{m}n_{d}^{x}=\sum_{a,b=1}^{N-1}n_{a}^{x}\left((n_{d}^{x}-\bm{\delta}_{a}^{x}+\bm{\delta}_{b}^{x})-n_{d}^{x}\right)=\sum_{b=1}^{N-1}(n_{b}^{x}-n_{d}^{x})

@@

Using equation \eqref{actionGraphRD} we have that $\forall x\in \{1,\ldots,L-1\}$ and $\forall d\in\{1,\ldots,N-1\}$

@@

	\mathcal{L}^{rd}n_{d}^{x}=\nu\sigma_{11}\Delta_{L}n_{d}^{x}+\nu\sigma_{12}\sum_{b=1\,:\,b\neq d}^{N-1}\Delta_{L}n_{c}^{x}+\Upsilon\sum_{b=1}^{N-1}(n_{c}^{x}-n_{\alpha}^{x})

@@

	\mathcal{L}^{rd}n_{d}^{1}=\sigma_{11}\nu \left(\rho_{d}^{1}-2n_{d}^{1}+n_{2}^{2}\right)+\sigma_{12}\nu\sum_{b=1\,:\,b\neq d}^{N-1}\left(\rho_{c}^{1}-2n_{c}^{1}+n_{c}^{2}\right)+\Upsilon\sum_{b=1\,:\,b\neq d}^{N-1}\left(n_{c}^{1}-n_{d}^{1}\right)
On the occupation variable $n_{d}^{L}$ the action is similar, but with the upper case $1$ replaced by $L$.\\ In the spirit of \cite{casini2022uphill} we can define the average density occupation of species $d$ at site $x$ as

@@

	\rho=\rho_{a}=\frac{\alpha}{\alpha_{N}+(N-1)\alpha}\quad \forall a\in \{1,\ldots,N-1\}\qquad \text{and}\qquad \rho_{N}=\frac{\alpha_{N}}{\alpha_{N}+(N-1)\alpha}

@@

	\Lambda_{rev}^{x}(n^{x})=\frac{\nu!}{\prod_{a=1}^{N}n_{a}^{x}!}\rho^{\sum_{a=1}^{N-1}n_{a}^{x}}\rho_{N}^{n_{N}^{x}}
This can be proved just by imposing the detailed balance conditions for the edge $x,x+1$ and for the boundary generators. For fixed edge $x\in \{1,\ldots,L\}$ we only prove the detailed balance for  $\mathcal{L}_{x,x+1}^{c}$ with $c\in\{1,\ldots,N-2\}$ since for the other generators the computation is similar. Consider the transition $\bm{n}\to \bm{n}-\delta_{a}^{x}+\delta_{g_{c}(b)}^{x}+\delta_{g_{c}(b)}^{x+1}-\delta_{b}^{x+1}$ for arbitrary $a,b,\in\{1,\ldots,N-1\}$; the detailled balance reads

@@

that is true if and only if $\rho_{a}=\rho$ $\forall a\in \{1,\ldots,N-1\}$.\\

@@

For the boundary transitions we have that, analogously to what happens for the multispecies stirring process, the reservoirs parameters must be such that $\beta_{a}=\alpha_{a}$.

@@

	\bm{\xi}=\left(\xi_{1}^{0},\ldots,\xi_{N}^{0}\right)\otimes\left(\xi_{1}^{x},\ldots,\xi_{N}^{x}\right)^{\otimes L}\otimes \left(\xi_{1}^{L+1},\ldots,\xi_{N}^{L+1}\right)

@@

and the component $\xi_{a}^{0}$  gives the number of dual particles of type $a\in \{1,\ldots,N\}$ at 

@@

	D(\bm{n},\bm{\xi})=\prod_{a=1}^{N-1}\left(\frac{\alpha_{a}}{|\alpha|}\right)^{\xi_{a}^{0}}\left(\prod_{x=1}^{L}\frac{(\nu -\sum_{a=2}^{N}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\right)\prod_{a=1}^{N-1}\left(\frac{\beta_{a}}{|\beta|}\right)^{\xi_{a}^{L+1}}

@@

Observe that the generator $\widetilde{\mathcal{L}}^{rd}$ has the same dynamics as $\mathcal{L}^{rd}$ in the bulk, while the boundaries are absorbing. 

@@

The duality between the boundary generators is trivial, because they have the same form of \eqref{siteDualGenerator}, up to a specific choice of the parameters. Therefore we only need to prove the duality relation for the bulk generator. 

@@

We need to prove that, for arbitrary $x\in\{1,\ldots,L\}$
	(\mathcal{H}_{x,x+1}^{rd})^{T}D&=D\mathcal{H}_{x,x+1}^{rd}\label{edgeDualityRelationRD}
That is equivalent of showing 

@@

Since the matrix $R_{x}$ is the same, we shall show that $\mathcal{H}_{x,x+1}^{c}$ and $\mathcal{H}_{x,x+1}^{m}$ have $\exp{(E^{x})}\exp{(E^{x})}$ as a symmetry. The first result will follow from the commutator between $\mathcal{H}_{x,x+1}^{c}$ and $\sum_{d=1}^{N-1}(E_{dN}^{x})\otimes \sum_{k=1}^{N-1}(E_{bN}^{x})$. Using \eqref{eq:comgl}, the bilinearity and associativity of the Kronecker product and the bilinearity of the brackets we obtain 

@@

@@

The steady state $|\Psi\rangle$ of the Hamiltonian $H$ is given by 
\begin{equation}\label{steadyStateH}
	|\Psi\rangle=\sum_{\tau_{1},\ldots,\tau_{L}=1}^{N}\Psi(\bm{\tau})|\bm{\tau}\rangle
\end{equation}
where for every $(\tau_{1},\ldots,\tau_{L})=\bm{\tau}$
\begin{equation}
	\begin{split}
		\Psi(\bm{\tau})&=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{\tau_{y}}^{(1-c_{y})(1-\delta_{\tau_{y},N})}
		\\&+
		\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{\tau_{q_{r}},N}\right) 
		\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{d_{q_{b}}=2}^{N}
		\\&
		\sum_{c_{1}=0}^{1-\delta_{\eta_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\eta_{L},N}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\eta_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{\eta_{y}}^{(1-c_{y})(1-\delta_{\eta_{y},N})}
	\end{split}
\end{equation}
where we have introduced, $\forall x\in \{1,\ldots,L\}$
\begin{equation}
	\eta_{x}(b)=\begin{cases}
		\tau_{x}\qquad &\text{if}\quad x\notin \{q_{1},\ldots,q_{b}\}\\
		d_{x}\qquad &\text{otherwise}
	\end{cases}%\qquad \theta_{x}=\begin{cases}
		%\tau_{x}\qquad &\text{if}\quad x\neq 1,\ldots,b\\
		%	1 \qquad &\text{otherwise}
		%\end{cases}
	\end{equation}
	The dependence of $\eta_{x}(b)$ with respect to $b$ is usually understood for the sake of notation. 
\begin{comment}
	{\color{blue}
		\begin{equation}\label{steadyStateH-coeff}
			\begin{split}
				\Psi(\bm{\tau})&=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{\tau_{y}}^{(1-c_{y})(1-\delta_{\tau_{y},N})}
				\\&+
				\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{s=1}^{b}\delta_{s_{q_{r}},N}\right) 
				\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{d_{q_{b}}=2}^{N}
				\\&
				\sum_{x=1\,:\, x\neq q_{1},\ldots,q_{b}}^{L}\sum_{c_{x}=0}^{1-\delta_{\tau_{x},N}}\sum_{c_{q_{1}}=1}^{1}\ldots\sum_{c_{q_{b}}=0}^{1}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(2+L)}
				\prod_{y=1\,:\, y\neq q_{1},\ldots,q_{b}}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}
				\\ &
				\beta_{\tau_{y}}^{(1-c_{y})(1-\delta_{\tau_{y},N})}
				\prod_{t=1}^{b}\lambda_{d_{q_{t}}}\left(2+L-q_{t}-\sum_{j=q_{t}}^{L}c_{j}\right)^{c_{q_{t}}}\beta_{d_{q_{t}}}^{(1-c_{q_{t}})}
			\end{split}
		\end{equation}
	}
\end{comment}
\newline \newline
	\textbf{Remark}: we observe that if no holes are present, i.e. if $\tau_{x}\neq N$ $\forall x\in \{1,\ldots,L\}$, then the second addend vanishes and
	\begin{equation}\label{LinkABS-corr}
		\Psi(\bm{\tau})=\Psi^{'}(\bm{\tau})
	\end{equation}
	When the configuration has holes, the presence of the second addend is motivated by the dependence of the "empty" in a fixed site from all others types in the same site.

	\paragraph{Proof of formula \eqref{steadyStateH}} As a consequence of \eqref{S1-Inverse}, we only need to show how the transformation $S_{1}^{-1}$ acts on the vector $|\Psi^{'}\rangle$. Here is more convenient to consider the matrix $\mathcal{S}_{1}^{-1}$ defined in \eqref{S2Gen}, acting on a single site, and make explicitly the tensor product over the chain. This matrix $\mathcal{S}_{1}$ is given by
	\begin{equation}\label{S1-L1}
		\mathcal{S}_{1}^{-1}=\sum_{\tau_{1}=1}^{N}e_{\tau_{1}}^{\tau_{1}}+(-1)\delta_{\tau_{1},N}\sum_{d_{1}=1}^{N-1}e_{1}^{d_{1}}
	\end{equation}
	Using the notation introduced in \eqref{notation1} and \eqref{notation2} we have that 
	\begin{equation}
		\begin{split}
			\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}&=\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}\right.
			\\&
			+\left.\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},N}\right)\sum_{d_{q_{1}}=1}^{N-1}\ldots\sum_{d_{q_{r}}=1}^{N-1}e_{\eta_{1},\ldots,\eta_{L}}^{\theta_{1},\ldots,\theta_{L}}\right\} 
		\end{split}
	\end{equation}
	where we have introduced, $\forall x\in \{1,\ldots,L\}$
	\begin{equation}
		%\eta_{x}=\begin{cases}
			%	\tau_{x}\qquad &\text{if}\quad x\neq 1,\ldots,b\\
			%	d_{x}\qquad &\text{otherwise}
			%\end{cases}\qquad
			\theta_{x}(b)=\begin{cases}
				\tau_{x}\qquad &\text{if}\quad x\notin \{q_{1},\ldots,q_{b}\}\\
				1 \qquad &\text{otherwise}
			\end{cases}
		\end{equation}
		The dependence of $\theta(b)$ with respect to $b$ is usually understood for the sake of notation. 
		This is proved by induction. Indeed, for $L=1$ it is trivially true, by \eqref{S1-L1}. We assume that it is true for arbitrary $L\in \mathbb{N}$ and we prove that it holds for $L+1$. 
		\begin{align*}
			\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}\otimes \mathcal{S}_{1}^{-1}&=
			\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}\right. \\&+\left. \sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},N}\right)\sum_{d_{q_{1}}=1}^{N-1}\ldots\sum_{d_{q_{r}}=1}^{N-1}e_{\theta_{1},\ldots,\theta_{L}}^{\eta_{1},\ldots,\eta_{L}}\right\}
			\\&\otimes
			\left\{ \sum_{\tau_{1}=1}^{N}e_{\tau_{L+1}}^{\tau_{L+1}}+(-1)\delta_{\tau_{L+1},N}\sum_{d_{L+1}=1}^{N-1}e_{1}^{d_{L+1}}\right\}
			\\&=
			\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L+1}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L+1}}^{\tau_{1},\ldots,\tau_{L+1}}\right. \\&+\left. \sum_{b=1}^{L+1}(-1)^{b}\sum_{q_{1}=1}^{L+1}\sum_{q_{2}=q_{1}+1}^{L+1}\ldots\sum_{q_{b}=q_{b-1}+1}^{L+1}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},N}\right)\sum_{d_{q_{1}}=1}^{N-1}\ldots\sum_{d_{q_{b}}=1}^{N-1}e_{\theta_{1},\ldots,\theta_{L+1}}^{\eta_{1},\ldots,\eta_{L+1}}\right\}
		\end{align*}
		\begin{comment}
